Supporting Information

### 2017-04-15 code/rmarkdown/supporting-information.Rmd
use pngs for figs update makefile update toml file

```{r, include=FALSE}
# set wd
knitr::opts_knit$set(root.dir = normalizePath("../.."))
```

@@

We conducted a benchmark analysis to understand how much time would be required to build and solve different sized conservation planning problems. Additionally, we also aimed to understand how the time required to execute a problem varied depending on which formulation was used (unreliable or reliable), and if fragmentation constraints were used.

@@

We generated simulated conservation planning data sets using varying number of features (`r paste(benchmark_parameters$number_of_features, collapse = ",")`) and planning units (`r paste(benchmark_parameters$number_of_planning_units, collapse = ",")`). For a given number of planning units and features, the data was simulated using the following steps. First, the planning units were simulated as squares that were arranged in a grid. All planning unit costs were set to one. The spatial distribution of features were generated using binary, spatially autocorrelated random fields [using the \texttt{RandomFields R} package; @r494; @r493]. If features were associated with less than two occupied planning units, these features were set to occupy two randomly selected planning units. All occupied planning units were set to have a probability of occupancy of `r benchmark_parameters$occupancy_probability`. Similar to the simulated data sets used in the main text, a geographic attribute space was used for each feature. The features' demand points were set as the centroids of the planning units that they occupied, and were weighted by the units' probability of occupancy. All problems used amount-based targets of `r benchmark_parameters$amount_target*100` % and space-based targets of `r benchmark_parameters$space_target*100`

We solved each conservation planning data set using the unreliable and reliable problem formulations (using default failure distance and level parameter) using no boundary length modifier, and using a boundary length modifier of `r max(benchmark_parameters$blm)`. To assess variation in execution times, we generated and solved `r benchmark_parameters$replicates` random data sets per combination of number of features and planning units. All conservation planning problems were solved to within `r general_parameters$MIPGap * 100` % of optimality using Gurobi (version 7.0.0) on a system with 64 GB RAM and an Intel(R) Xeon (R) CPU (E5-2630 v3; 2.40 GHz). All problems were solved using a single thread.

@@

The benchmark analysis revealed that moderately-sized conservation problems can be solved in a relatively short period of time (Figure S2). As predicted, problems were solved much quicker when using the unreliable formulation than when using the reliable formulation. Additionally, the solve times varied substantially for different data sets with the same properties (ie. number of features and planning units). This result suggests that it may difficult to estimate exactly how long a given problem will take to solve.

We were not able to explore how long large-sized problems would take to solve because our computer system did not have enough memory. One method to reduce the problem size would be to simply use less demand points. Another method to reduce problem size would be to set a maximum distance between demand points and planning units such that demand points cannot be represented by planning units that that are too far away. Both of these method could be applied using functions provided in the \texttt{raptr R} package. Future research is needed to explore these methods and understand how the impact solution quality. Additionally, future research could involve implementing more advanced methods to solve the optimization problems [eg. as described in @r16; @r15].

>>>>

```{r, include=FALSE}
knitr::opts_knit$set(root.dir = normalizePath("../.."))
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo"), dpi = 500)
```

@@

We conducted a benchmark analysis to understand how much time would be required to solve different sized problems using the \texttt{raptr R} package.

@@

We simulated conservation planning data sets containing different numbers of features and planning units (see Figure S2 for amounts). For a given number of planning units and features, a data set was simulated using the following steps. First, the planning units were simulated as squares that were arranged in a grid. Second, the planning unit costs were set to one. Third, the spatial distribution of each feature in the planning units were simulated using binary, spatially autocorrelated random fields [using the \texttt{RandomFields R} package; @r494; @r493]. Fourth, if a feature was found to occupy less than two planning units, the feature was set to occupy two randomly selected planning units. All occupied planning units were set to have a probability of occupancy of `r benchmark_parameters$occupancy_probability` for all features. Fifth, similar to the simulated data sets described in the main text, a geographic attribute space was generated for each feature. The features' demand points were set as the centroids of the planning units that they occupied, and were weighted by the units' probability of occupancy. After simulating the data sets, solutions were generated using the \texttt{raptr R} package and Gurobi (version 7.0.2).

We generated solutions for the conservation planning data sets using different formulations and parameters. Specifically, the solutions were generated using the unreliable and reliable formulation, and several boundary length multipliers (`r paste(unique(benchmark_parameters$blm), sep = "and")`). The solutions were generated using amount-based targets of `r benchmark_parameters$amount_target*100` % and space-based targets of `r benchmark_parameters$space_target*100`. To assess variation in solve times, we generated and solved `r benchmark_parameters$replicates` random data sets per combination of number of features and planning units. All problems were solved to within `r general_parameters$MIPGap * 100` % of optimality and were solved using a single thread on a system with 64 GB RAM and an Intel(R) Xeon (R) CPU (E5-2630 v3; 2.40 GHz).

@@

The benchmark analysis revealed that moderately-sized conservation problems can be solved in a relatively short period of time (Figure S2). Problems were solved much quicker when using the unreliable formulation than when using the reliable formulation. The solve times could be reduced by using more threads.  We were not able to determine how long problems containing over 100 planning units would take to solve using the reliable formulation because the system did not contain enough would take to solve because our computer system did not have enough RAM. Future research could involve implementing more advanced methods to solve the optimization problems [eg. as described in @r16; @r15].
